Using Metric Space Indexing for Complete and Efficient Record Linkage

### 2017-11-21 paper.tex
Update on Overleaf.

\usepackage{url}
\usepackage{hyperref}
\usepackage{cleveref}
\usepackage{hhline}

@@

In some circumstances, incomplete approaches such as blocking can yield
higher precision than complete techniques. This can occur when the
datasets contain a significant number of non-matches that nonetheless
have high similarity. In this situation, the fact that an incomplete
technique omits consideration of some potential links can serve to
improve precision, since a classification decision based on similarity
threshold is incorrect for high-similarity non-matches. By definition,
recall is never higher for incomplete techniques.

@@

@@

\begin{figure}
\includegraphics[width=\textwidth]{figures/plotBQ_--_Cora_-_Brute_Force}
\caption{Linkage quality on Skye dataset using M-tree\label{skye-quality-mtree}}
\end{figure}

\begin{figure}
\includegraphics[width=\textwidth]{figures/plotBQ_--_Cora_-_MTree}
\caption{Linkage quality on Kilmarnock dataset using M-tree\label{kilmarnock-quality-mtree}}
\end{figure}

@@

In this paper we have demonstrated the efficacy of MSI in achieving consistently complete and efficient record linkage, without the need for complex parameter tuning. In conclusion, this assertion deserves some careful unpacking. It is always possible to achieve high quality linkage using a brute-force approach. However the n-squared complexity of this approach prevents its practical application for datasets of even moderate size. The use of MSI techniques such as M-tree delivers the same results as the brute-force approach with fewer comparisons. We have shown that the M-tree approach delivers high precision, high recall results that are the same as those delivered by the brute-force approach. Furthermore this is achieved consistently without the need for complex parameter tuning.

@@

However, this paper also highlights some unexpected results. Firstly, the good quality results yielded by both traditional blocking and LSH are partly due to the fact that (in the limit) they tend towards brute-force as the number of records in the block increase. A second unexpected result is that shown in \Cref{fig-cora-brute}, namely that LSH can yield higher precision than is achieved by a complete method such as M-Tree. This is due to complex reasons .... \emph{TODO EXPAND HERE}.

>>>>

\usepackage{url}
\usepackage{hyperref}
\usepackage{cleveref}
\usepackage{hhline}
\usepackage{caption}
\usepackage{subcaption}

@@

@@

In some circumstances, incomplete approaches such as traditional blocking and LSH-MinHash can yield
higher precision than complete techniques. This can occur when the
datasets contain a significant number of non-matches that nonetheless
have high similarity. In this situation, the fact that an incomplete
technique omits consideration of some potential links can serve to
improve precision, since a classification decision based on similarity
threshold is incorrect for high-similarity non-matches. By definition,
recall is never higher for incomplete techniques.

@@

\begin{figure}
\centering
\begin{subfigure}{.5\textwidth}
  \centering
\includegraphics[width=\textwidth]{figures/skye-mtree}
\caption{Linkage quality on Skye dataset using M-tree\label{skye-quality-mtree}}
\end{subfigure}%
\begin{subfigure}{.5\textwidth}
  \centering
\includegraphics[width=\textwidth]{figures/kili-mtree}
\caption{Linkage quality on Kilmarnock dataset using M-tree\label{kilmarnock-quality-mtree}}
\end{subfigure}
\caption{M-Tree based linkage on the demographic data sets}
\label{demography-quality-mtree}
\end{figure}

@@

In this paper we have demonstrated the efficacy of MSI in achieving  complete and efficient record linkage, without the need for complex parameter tuning. In conclusion, this assertion deserves some careful unpacking. It is always possible to achieve high quality linkage using a brute-force approach. However the n-squared complexity of this approach prevents its practical application for datasets of even moderate size. The use of MSI techniques such as M-tree delivers the same results as the brute-force approach with fewer comparisons. We have shown that the M-tree approach delivers high precision, high recall results that are the same as those delivered by the brute-force approach. Furthermore this is achieved consistently without the need for complex parameter tuning.

@@

However, this paper also highlights some unexpected results. Firstly, the good quality results yielded by both traditional blocking and LSH are partly due to the fact that (in the limit) they tend towards brute-force as the number of records in the block increase. A second unexpected result is that shown in \Cref{fig-cora-brute}, namely that LSH can yield higher precision than is achieved by a complete method such as M-Tree as was discussed in Sect.~\ref{sec-approach}.

\emph{IS THIS RIGHT?}.
